Updates on the Exoplanet Orbit Database

### 2014-01-24 draft/ms.tex

KEPID: For KOIs, the Exoplanet Archive reports Kepler ID.

@@

EOD: Planets discovered by radial velocity and transit method are classified as EOD planets. They have robust orbital parameters such as PER, ECC, K, OM, and I.

MICROLENSING, IMAGING, TIMING and ASTROMETRY: We have added MICROLENSING, IMAGING, TIMING and ASTROMETRY fields for planets discovered by methods other than radial velocity and transit. These planets are categorized as ``Other Planets'' on exoplanets.org

>>>>

KEPID: None of EOD planets has KEPID! This is just something we copied
from Exoplanet Archive...

@@

EOD: Planets discovered by radial velocity and transit method are
classified as EOD planets. They have robust orbital parameters such as
PER, ECC, K, OM, and I. \textit{(Sharon's comments: You don't need to
  describe why we include a planet in EOD -- this is covered at the
  beginning of Section~\ref{sec:update} as we discuss the `scope of
  EOD'. Just say what this flag is. Also, right now it includes RV,
  Transit, and also some Timing planets. The first sentence sounds
  like as long as a planet is discovered via RV and transit, it'll be
  in EOD, which is not true, I think.)}

MICROLENSING, IMAGING, TIMING and ASTROMETRY: We have added MICROLENS-
ING, IMAGING, TIMING and ASTROMETRY fields for planets discovered by
methods other than radial velocity and transit. These planets are
categorized as ``Other Planets'' on exoplanets.org. \textit{(Sharon's
  comments: Instead of saying `discovered', we should say `detected'
  -- some planets are detected by these methods but are not
  necessarily discovered by them at the first place. Re-phrase the
  last sentence -- not all of planets with any of these TRUE are in
  `Other Planets', only some are, so maybe just note planets
  discovered by these methods are not necessarily in EOD and direct
  the reader to Section~\ref{sec:kepler} where we talk about `Other
  Planets'. Remember Section~\ref{sec:update} is focuses on EOD
  updates though the fields apply to all planets on
  exoplanets.org. Need to note here that we require the detection to
  be robust, as determined by the QUAlity Control Board of the
  Exoplanet Database, QUACBED.)}
